Draft: Notes on the revised Hidden weight function

### 2024-09-26 RevisedHiddenWeight.tex
Added Walsh bound comparison

\begin{remark}
    There are still instances where $\Dnka nka=0$ which have not been described by the above. For instance, we have $\Dnka{34}4a=0$ if $\{p,q\}=\{1,2\}$.
\end{remark}
>>>>>>> 927bf10bd354d63e33833a2cff7df1af6d3d3523

@@

Table \ref{table:max_walsh_vs_bound} compares $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ to the upper bound $B_n$ we find using the above method. Table \ref{table:walsh_bounds} gives all values of this bound $B_n$ for all even $1\leq n\leq 80$. As we can see from Figure \ref{fig:walsh_bound}, our bound $B_n$ is exponential in $n$.

@@

\pmnote{@Tim, could you do a (summary) graph with the bound it gives for the nonlinearity? (Definition from the Walsh transform in the preliminaries)

Could you add curves for the majority function, $n$ even $\NL=2^{n-1}- 1/2 \binom{n}{n/2}$ , and HWBF  $n$ even $\NL=2^{n-1}- 2 \binom{n-2}{(n-2)/2}$ \cite{DAM:WCST14} Theorem 3.

}

Here is the updated table with the new values for \( B_n \) corresponding to each \( n \):

\begin{table}
    \centering
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $2$  & $4.00 \cdot 10^{0}$  \\
            $4$  & $1.40 \cdot 10^{1}$  \\
            $6$  & $3.60 \cdot 10^{1}$  \\
            $8$  & $1.14 \cdot 10^{2}$  \\
            $10$ & $2.88 \cdot 10^{2}$  \\
            $12$ & $8.20 \cdot 10^{2}$  \\
            $14$ & $2.32 \cdot 10^{3}$  \\
            $16$ & $6.01 \cdot 10^{3}$  \\
            $18$ & $1.82 \cdot 10^{4}$  \\
            $20$ & $4.85 \cdot 10^{4}$  \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $22$ & $1.40 \cdot 10^{5}$  \\
            $24$ & $3.92 \cdot 10^{5}$  \\
            $26$ & $1.14 \cdot 10^{6}$  \\
            $28$ & $3.12 \cdot 10^{6}$  \\
            $30$ & $8.90 \cdot 10^{6}$  \\
            $32$ & $2.50 \cdot 10^{7}$  \\
            $34$ & $7.14 \cdot 10^{7}$  \\
            $36$ & $2.04 \cdot 10^{8}$  \\
            $38$ & $5.75 \cdot 10^{8}$  \\
            $40$ & $1.62 \cdot 10^{9}$  \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $42$ & $4.59 \cdot 10^{9}$  \\
            $44$ & $1.29 \cdot 10^{10}$ \\
            $46$ & $3.63 \cdot 10^{10}$ \\
            $48$ & $1.02 \cdot 10^{11}$ \\
            $50$ & $2.88 \cdot 10^{11}$ \\
            $52$ & $8.06 \cdot 10^{11}$ \\
            $54$ & $2.30 \cdot 10^{12}$ \\
            $56$ & $6.45 \cdot 10^{12}$ \\
            $58$ & $1.83 \cdot 10^{13}$ \\
            $60$ & $5.14 \cdot 10^{13}$ \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $62$ & $1.47 \cdot 10^{14}$ \\
            $64$ & $4.09 \cdot 10^{14}$ \\
            $66$ & $1.17 \cdot 10^{15}$ \\
            $68$ & $3.25 \cdot 10^{15}$ \\
            $70$ & $9.34 \cdot 10^{15}$ \\
            $72$ & $2.60 \cdot 10^{16}$ \\
            $74$ & $7.44 \cdot 10^{16}$ \\
            $76$ & $2.08 \cdot 10^{17}$ \\
            $78$ & $5.97 \cdot 10^{17}$ \\
            $80$ & $1.65 \cdot 10^{18}$ \\
            \hline
        \end{tabular}
    \end{minipage}
    \caption{Values of $B_n$ for various $n$}
    \label{table:walsh_bounds}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=10cm]{walsh_bound}
    \caption{Our bounds $B_n$ in terms of $n$, on a logarithmic scale}
    \label{fig:walsh_bound}
\end{figure}

@@

	\begin{align*}
	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t} \atop z \in \Ekn{k-\ell}{n-2t}} (-1)^{d_{t,t}(y)+by +cz}\\
	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.
	\end{align*}

@@

\begin{proposition}[Algebraic immunity of $f$]
	Let $n\in \N$ be even, $f$ defined as
	$f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k$ and $h$ denote the $n$-variable HWBF, the following holds:
	\[\AI(f)\ge \AI(h)-2.\]
\end{proposition}
\begin{proof}
	Let denote by $q$ the quadratic function $\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$, it allows to write $h=f+q$. 
	Let $g\neq 0$ be an annihilator of $f+ \varepsilon$ of minimum degree (where $\varepsilon \in \{0,1\}$), then the following holds:
	\[g (1+q) (h+\varepsilon) = g(1+q) (f+\varepsilon + q)=0, \]
	hence $g (1+q)$ is an annihilator of $h+ \varepsilon$. 
	If $g (1+q)\ne 0$ then $\degg(g(1+q)) \le \degg(g)+2$ and we obtain $\degg(g)\ge \AI(h) -2$. 
	Otherwise, $g (1+q)= 0$ implies that $g$ annihilates $1+q$ and therefore $0=g (f+\varepsilon + 1 +q)=g(h+ \varepsilon +1)$ that is $\degg(g)\ge \AI(h)$. 
	Summarizing, for any non null annihilator $g$ of $f$ or $f+1$ we get $\degg(g)\ge \AI(h)-2$, it allows to conclude $\AI(f)\ge \AI(h)-2$.

>>>>

\begin{remark}
    There are still instances where $\Dnka nka=0$ which have not been described by the above. For instance, we have $\Dnka{34}4a=0$ if $\{p,q\}=\{1,2\}$.
\end{remark}

@@

Table \ref{table:max_walsh_vs_bound} compares $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ to the upper bound $B_n$ we find using the above method. Table \ref{table:walsh_bounds} gives all values of this bound $B_n$ for all even $1\leq n\leq 80$.

@@

Figure \ref{fig:walsh_bound_comparison} compares our experimental bound $B_n$ to the theoretical bound $n\cdot 2^{3n/4}+1$ and the binomial coefficient $\binom{n}{n/2}$, on a logarithmic scale. The first two and the last one have an asymptotic slope of $3/4$ and $1$, respectively.

\begin{figure}
    \centering
    \includegraphics[width=9cm]{comparison_walsh_bound.pdf}
    \caption{On a logarithmic scale, our experimental bound $B_n$ in terms of $n$ in red, our theoretical bound $n\cdot 2^{3n/4}+1$ from Property \ref{prop:bound_sum_D_nka} in green, and the bound $\binom{n}{n/2}$ in blue.}
    \label{fig:walsh_bound_comparison}
\end{figure}

\begin{table}
    \centering
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $\approx B_n$ \\
            \hline
            $2$  & $4.00 \cdot 10^{0}$  \\
            $4$  & $1.40 \cdot 10^{1}$  \\
            $6$  & $3.60 \cdot 10^{1}$  \\
            $8$  & $1.14 \cdot 10^{2}$  \\
            $10$ & $2.88 \cdot 10^{2}$  \\
            $12$ & $8.20 \cdot 10^{2}$  \\
            $14$ & $2.32 \cdot 10^{3}$  \\
            $16$ & $6.01 \cdot 10^{3}$  \\
            $18$ & $1.82 \cdot 10^{4}$  \\
            $20$ & $4.85 \cdot 10^{4}$  \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $\approx B_n$ \\
            \hline
            $22$ & $1.40 \cdot 10^{5}$  \\
            $24$ & $3.92 \cdot 10^{5}$  \\
            $26$ & $1.14 \cdot 10^{6}$  \\
            $28$ & $3.12 \cdot 10^{6}$  \\
            $30$ & $8.90 \cdot 10^{6}$  \\
            $32$ & $2.50 \cdot 10^{7}$  \\
            $34$ & $7.14 \cdot 10^{7}$  \\
            $36$ & $2.04 \cdot 10^{8}$  \\
            $38$ & $5.75 \cdot 10^{8}$  \\
            $40$ & $1.62 \cdot 10^{9}$  \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $\approx B_n$ \\
            \hline
            $42$ & $4.59 \cdot 10^{9}$  \\
            $44$ & $1.29 \cdot 10^{10}$ \\
            $46$ & $3.63 \cdot 10^{10}$ \\
            $48$ & $1.02 \cdot 10^{11}$ \\
            $50$ & $2.88 \cdot 10^{11}$ \\
            $52$ & $8.06 \cdot 10^{11}$ \\
            $54$ & $2.30 \cdot 10^{12}$ \\
            $56$ & $6.45 \cdot 10^{12}$ \\
            $58$ & $1.83 \cdot 10^{13}$ \\
            $60$ & $5.14 \cdot 10^{13}$ \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $\approx B_n$ \\
            \hline
            $62$ & $1.47 \cdot 10^{14}$ \\
            $64$ & $4.09 \cdot 10^{14}$ \\
            $66$ & $1.17 \cdot 10^{15}$ \\
            $68$ & $3.25 \cdot 10^{15}$ \\
            $70$ & $9.34 \cdot 10^{15}$ \\
            $72$ & $2.60 \cdot 10^{16}$ \\
            $74$ & $7.44 \cdot 10^{16}$ \\
            $76$ & $2.08 \cdot 10^{17}$ \\
            $78$ & $5.97 \cdot 10^{17}$ \\
            $80$ & $1.65 \cdot 10^{18}$ \\
            \hline
        \end{tabular}
    \end{minipage}
    \caption{Approximate values of $B_n$ for various $n$}
    \label{table:walsh_bounds}
\end{table}

@@

	\begin{align*}
	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
	&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,t}(y)+by +cz}\\
	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
	\end{align*}

@@

\begin{proposition}[Algebraic immunity of $f$]
	Let $n\in \N$ be even, $f$ defined as
	$f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k$ and $h$ denote the $n$-variable HWBF, the following holds:
	\[\AI(f)\ge \AI(h)-2.\]
\end{proposition}
\begin{proof}
	Let denote by $q$ the quadratic function $\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$, it allows to write $h=f+q$. 
	Let $g\neq 0$ be an annihilator of $f+ \varepsilon$ of minimum degree (where $\varepsilon \in \{0,1\}$), then the following holds:
	\[g (1+q) (h+\varepsilon) = g(1+q) (f+\varepsilon + q)=0, \]
	hence $g (1+q)$ is an annihilator of $h+ \varepsilon$. 
	If $g (1+q)\ne 0$ then $\degg(g(1+q)) \le \degg(g)+2$ and we obtain $\degg(g)\ge \AI(h) -2$. 
	Otherwise, $g (1+q)= 0$ implies that $g$ annihilates $1+q$ and therefore $0=g (f+\varepsilon + 1 +q)=g(h+ \varepsilon +1)$ that is $\degg(g)\ge \AI(h)$. 
	Summarizing, for any non null annihilator $g$ of $f$ or $f+1$ we get $\degg(g)\ge \AI(h)-2$, it allows to conclude $\AI(f)\ge \AI(h)-2$.
\end{proof}
